Normalized Coherence

### 2020-03-17 Analysis/03_Normalized_Coherence.Rmd
Add raw slopes in addition to their CIs

>>>>

# Merging together the confidence intervals

```{r}
#Renaming names before joining and manipulating

#BIOGRID
dis_slopes_biogrid_count = dis_slopes_biogrid_count %>% ungroup() %>% dplyr::select(-Count) %>% dplyr::rename(`Biogrid Slope` = Slope)
dis_slopes_biogrid_ci = dis_slopes_biogrid_ci %>% ungroup() %>% dplyr::select(-Count) %>% dplyr::rename(`Biogrid Lower` = Lower, `Biogrid Upper` = Upper)
dis_slopes_biogrid <- full_join(dis_slopes_biogrid_count, dis_slopes_biogrid_ci, by = c("Disease", "Category"))

#STRING
dis_slopes_string_count = dis_slopes_string_count %>% dplyr::rename(`String Slope` = Slope)
dis_slopes_string_ci = dis_slopes_string_ci %>% ungroup() %>% dplyr::select(-Count) %>% dplyr::rename(`String Lower` = Lower, `String Upper` = Upper)
dis_slopes_string <- full_join(dis_slopes_string_count, dis_slopes_string_ci, by = c("Disease", "Category"))

#STRING Filtered
dis_slopes_string_filt_count = dis_slopes_string_filt_count %>% ungroup() %>% dplyr::select(-Count) %>% dplyr::rename(`String Filt Slope` = Slope)
dis_slopes_string_filt_ci = dis_slopes_string_filt_ci %>% ungroup() %>% dplyr::select(-Count) %>% dplyr::rename(`String Filt Lower` = Lower, `String Filt Upper` = Upper)
dis_slopes_string_filt <- full_join(dis_slopes_string_filt_count, dis_slopes_string_filt_ci, by = c("Disease", "Category"))

#Biogrid and STRING
ci = full_join(dis_slopes_biogrid, dis_slopes_string, by = c("Disease", "Category"))

#Merging in STRING Filtered
ci = full_join(ci, dis_slopes_string_filt, by = c("Disease", "Category"))

write.csv(ci, '../manuscript/Tables/Confidence_Intervals.csv', quote = FALSE)
```
